FINE SCALE REGISTRATION OF SIDEWALKS AND OTHER RIBBON-LIKE FEATURES FROM AERIAL IMAGERY

### 2018-07-26 Chapters/3.Hypothesis/Hypothesis.tex
Updates from ShareLaTeX

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/ribbon-3d.pdf}
    \caption[3D Ribbon Image]{An illustration of the parameters for a ribbon; the $r$ axis captures the thickness of the ribbon and the $s$ axis captures the distance along the initial ribbon. The $t$ axis records horizontal displacements from the initial ribbon's medial curve.}
    \label{fig:ribbon_3d}
\end{figure}

>>>>

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=\textwidth]{Figures/ribbon-3d.pdf}
%     \caption[3D Ribbon Image]{An illustration of the parameters for a ribbon; the $r$ axis captures the thickness of the ribbon and the $s$ axis captures the distance along the initial ribbon. The $t$ axis records horizontal displacements from the initial ribbon's medial curve.}
%     \label{fig:ribbon_3d}
% \end{figure}

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.95\columnwidth]{Figures/ribbon-3d-combined.pdf}
    \caption[3D Ribbon Image]{An illustration of the parameters for a ribbon: (top) the $k$ axis captures the thickness of the ribbon and the $i$ axis captures the distance along the initial ribbon, the $j$ axis records horizontal displacements from the initial ribbon's medial curve; (bottom) the boundaries of the ribbon must lie within $\pm \MaxDistance{}$, pixels within $\pm \MinRadius{}$ of the center are probably part of the ribbon and pixels further than $\pm \MaxRadius{}$ are likely negative. }
    \label{fig:ribbon_3d}
\end{figure}

### 2018-07-26 Chapters/3.Hypothesis/Paper.tex
Updates from ShareLaTeX

We do not in general have a reliable estimate for the initial radius of our ribbon, 
but we can construct a trimap (\figref{fig:ribbon_3d_2}, bottom), as is done by \GrabCut{}, in order to estimate $\theta$. We choose a distance $\MaxDistance$ and numbers $\MinRadius < \MaxRadius$ 
so that all pixels with a distance of $[0, \MinRadius)$ are likely part of the ribbon (positive), all pixels within a distance of $[\MinRadius, \MaxRadius)$ are unknown, and others are are assumed not to be part of the ribbon (negative); 
In our experiments we chose  $\MaxRadius$ as twice the expected mean width of ribbons (e.g. 2 meters), $\MinRadius = \MaxRadius/2$, and $\MaxDistance=\MaxRadius+\MinRadius$.  
In figure \ref{fig:ribbon_3d_2} these regions correspond to strips of pixels in $\RibbonImage{}$ along the edges and center of the image.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.95\columnwidth]{Figures/ribbon-3d-combined.pdf}
    \caption[3D Ribbon Image 2]{An illustration of the parameters for a ribbon: (top) the $k$ axis captures the thickness of the ribbon and the $i$ axis captures the distance along the initial ribbon, the $j$ axis records horizontal displacements from the initial ribbon's medial curve; (bottom) the boundaries of the ribbon must lie within $\pm \MaxDistance{}$, pixels within $\pm \MinRadius{}$ of the center are probably part of the ribbon and pixels further than $\pm \MaxRadius{}$ are likely negative. }
    \label{fig:ribbon_3d_2}
\end{figure}

>>>>

We do not in general have a reliable estimate for the initial radius of our ribbon, 
but we can construct a trimap (\figref{fig:ribbon_3d}, bottom), as is done by \GrabCut{}, in order to estimate $\theta$. We choose a distance $\MaxDistance$ and numbers $\MinRadius < \MaxRadius$ 
so that all pixels with a distance of $[0, \MinRadius)$ are likely part of the ribbon (positive), all pixels within a distance of $[\MinRadius, \MaxRadius)$ are unknown, and others are are assumed not to be part of the ribbon (negative); 
In our experiments we chose  $\MaxRadius$ as twice the expected mean width of ribbons (e.g. 2 meters), $\MinRadius = \MaxRadius/2$, and $\MaxDistance=\MaxRadius+\MinRadius$.  
In figure \ref{fig:ribbon_3d} these regions correspond to strips of pixels in $\RibbonImage{}$ along the edges and center of the image.

@@
